---
always_allow_html: yes
output:
  html_document: default
params:
  data.directory: "../../data/input/ze!nonquot"
  data.collection: !r tolower(c("ZEI010BD1.TXT"))
  data.params: NULL
  data.template: !r c("bdf.bsme2.req")
  lang: "EN"
  numpage: 20
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
knitr::read_chunk("../../R/tool.R")
knitr::read_chunk("../../R/data.R")
knitr::read_chunk("../../R/ccze_init.R")
knitr::read_chunk("../../R/ccze_footer.R")
```
```{r}
<<init>>
<<tool>>
<<data>>
```
```{r include=T}
includeCSS("../../css/ccze.css")
```
```{r}
data.collection <- getDataCollection()
```

## `r ifelse(params$lang=="FR","Indicateurs de performances au sein de la Zone euro","Performance indicators within the Euro area")`

***
<p class="unitlegend">*`r ifelse(params$lang=="FR","Variation en pourcentage","Percentage change")`*</p>
<p class="titlechart title">**`r ifelse(params$lang=="FR","Co&ucirc;t total horaire de la main-d'&oelig;uvre","Hourly labour cost")`** *`r tags$sup("(a)(b)")`*</p>

```{r}

#get data & metadata
data <- getData(data.collection,params$data.collection[1])[[2]]
meta <- getData(data.collection,params$data.collection[1])[[1]]

#select series
series <- c(1, #variable
            2, #France
            3, #Germany
            5, #Spain
            8, #Euro area
            4, #Belgium
            6, #Italy
            7) #Netherlands 

#set date periods to quarter format
data$date <- format(as.yearqtr(data$date,"%Y-%m"),ifelse(params$lang=="FR",
                                                        "T%q %Y",
                                                        "%Y Q%q"))

#keep current year + 7 previous whole years
end.period <- tail(grep(ifelse(params$lang=="FR","T1","Q1"),data$date),1)
begin.period <- end.period-28
end.period <- length(data$date)
periods <- rev(seq(end.period,begin.period,-1))
dat <- data[periods,series]
rm(begin.period,end.period)

#set metadata
met <- as.character(meta[2,series])
met <- trimws(unlist(lapply(strsplit(met,":"),"[[",1)))
met <- countrynameFR2EN(met)

#min and max of Y-Axis for the two charts
c_max <- ceiling(max(dat[,-c(1)]))
c_min <- floor(min(dat[,-c(1)]))

#chart 1
c1 <- highchart(width=450) %>%
  hc_exporting(enabled=T, filename = "bdf_ccze",buttons=exporting.buttons) %>%
  hc_colors(c(style.color.FR,style.color.DE,style.color.ES,style.color.EA,style.color.BE,style.color.IT,style.color.NL)) %>%
  hc_plotOptions(line=list(marker=list(enabled=F))) %>%
  hc_tooltip(valueDecimals=1,shared=T,valueSuffix=" %",
             pointFormat=style.point.format, headerFormat=style.header.format) %>%
  hc_legend(align="right",x=10,itemDistance=25) %>%
  hc_xAxis(categories=dat[,1],
           labels=list(formatter=JS("function () {
                var label=(this.value).toString();
                var res=(label.replace(' ','<br>')).replace(/\\d{2}(?=\\d{2})/,'');
                return res;
            }")),
           gridLineWidth=1,tickInterval=4) %>%
  hc_yAxis(min=c_min,max=c_max,startOnTick=F,endOnTick=F,allowDecimals=F,minPadding=0,maxPadding=0,tickInterval=1) %>%
  hc_add_series(name=met[2],data=dat[,2], id=met[2], lineWidth=3) %>%
  hc_add_series(name=met[3],data=dat[,3], id=met[3]) %>%
  hc_add_series(name=met[4],data=dat[,4], id=met[4]) %>%
  hc_add_series(name=met[5],data=dat[,5], id=met[5], lineWidth=3) %>%
  hc_add_series(name=met[6],id=met[6],showInLegend=F) %>% #fake series (for sharing legend)
  hc_add_series(name=met[7],id=met[7],showInLegend=F) %>%
  hc_add_series(name=met[8],id=met[8],showInLegend=F)
  
#chart 2
c2 <- c1 %>%
  hc_legend(align="left",itemDistance=25) %>%
  hc_yAxis_multiples(
    list(min=c_min,max=c_max,startOnTick=F,endOnTick=F,allowDecimals=F,minPadding=0,maxPadding=0,
         tickInterval=1,title=list(text=NULL)),
    list(linkedTo=0,opposite=T,title=list(text=NULL))) %>%
  hc_colors(c(style.color.EA,style.color.BE,style.color.IT,style.color.NL)) %>%
  hc_rm_series(name=c(met[2],met[3],met[4],met[5],met[6],met[7],met[8])) %>%
  hc_add_series(name=met[5],data=dat[,5], id=met[5],lineWidth=3, showInLegend=F) %>%
  hc_add_series(name=met[6],data=dat[,6], id=met[6]) %>%
  hc_add_series(name=met[7],data=dat[,7], id=met[7]) %>%
  hc_add_series(name=met[8],data=dat[,8], id=met[8])

#share the legend between the charts
c1 <- c1 %>%
  hc_plotOptions(series = list(events = list(legendItemClick = sharelegend)))

#---charts 3 & 4:

#select series
series <- c(1, #variable
            9, #France
            10, #Germany
            12, #Spain
            15, #Euro area
            11, #Belgium
            13, #Italy
            14) #Netherlands 

#keep current year + 7 previous whole years
dat <- data[periods,series]
rm(periods)

#set metadata
met <- as.character(meta[2,series])
met <- trimws(unlist(lapply(strsplit(met,":"),"[[",1)))
met <- countrynameFR2EN(met)

#min and max of Y-Axis for the two charts
c_max <- ceiling(max(dat[,-c(1)]))
c_min <- floor(min(dat[,-c(1)]))

#ouput the charts in HTML
div(class = "hc-link-legend",
    tags$table(
      tags$tr(
        tags$td(c1),
        tags$td(c2))
    )
)

```

<p>&nbsp;</p>
<p class="titlechart">**`r ifelse(params$lang=="FR","Co&ucirc;t salarial horaire","Hourly wage cost")`** *`r tags$sup("(b)")`*</p>

```{r}

#chart 3
c3 <- c1 %>%
  hc_yAxis(min=c_min,max=c_max,startOnTick=F,endOnTick=F,allowDecimals=F,minPadding=0,maxPadding=0,tickInterval=1) %>%
  hc_rm_series(name=c(met[2],met[3],met[4],met[5],met[6],met[7],met[8])) %>%
  hc_add_series(name=met[2],data=dat[,2], id=met[2], lineWidth=3) %>%
  hc_add_series(name=met[3],data=dat[,3], id=met[3]) %>%
  hc_add_series(name=met[4],data=dat[,4], id=met[4]) %>%
  hc_add_series(name=met[5],data=dat[,5], id=met[5], lineWidth=3) %>%
  hc_add_series(name=met[6],id=met[6],showInLegend=F) %>% #fake series (for sharing legend)
  hc_add_series(name=met[7],id=met[7],showInLegend=F) %>%
  hc_add_series(name=met[8],id=met[8],showInLegend=F)

#chart 4
c4 <- c3 %>%
  hc_legend(align="left",itemDistance=25) %>%
  hc_yAxis_multiples(
    list(min=c_min,max=c_max,startOnTick=F,endOnTick=F,allowDecimals=F,minPadding=0,maxPadding=0,
         tickInterval=1,title=list(text=NULL)),
    list(linkedTo=0,opposite=T,title=list(text=NULL))) %>%  
  hc_colors(c(style.color.EA,style.color.BE,style.color.IT,style.color.NL)) %>%
  hc_rm_series(name=c(met[2],met[3],met[4],met[5],met[6],met[7],met[8])) %>%
  hc_add_series(name=met[5],data=dat[,5], id=met[5],lineWidth=3, showInLegend=F) %>%
  hc_add_series(name=met[6],data=dat[,6], id=met[6]) %>%
  hc_add_series(name=met[7],data=dat[,7], id=met[7]) %>%
  hc_add_series(name=met[8],data=dat[,8], id=met[8])

#ouput the charts in HTML
div(class = "hc-link-legend",
    tags$table(
      tags$tr(
        tags$td(c3),
        tags$td(c4))
    )
)

```{r eval = T}
<<footer>>
```


