---
always_allow_html: yes
output:
  html_document: default
params: 
  lang: "FR"
  numpage: 19
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
knitr::read_chunk("../../R/tool.R")
knitr::read_chunk("../../R/data.R")
knitr::read_chunk("../../R/ccze_init_table.R")
knitr::read_chunk("../../R/ccze_footer.R")
```
```{r}
<<init>>
<<tool>>
<<data>>
```
```{r include=T}
includeCSS("../../css/ccze.css")
```
```{r}
data.collection <- getDataCollection("../../data/input/ze!nonquot")
```

## `r ifelse(params$lang=="FR","Indicateurs de performances au sein de la Zone euro","Performance indicators within the Euro area")`

***
<p class="unitlegend">*`r ifelse(params$lang=="FR","Variation en pourcentage","Percentage change")`*</p>
<p class="titlechart title">**`r ifelse(params$lang=="FR","Co&ucirc;t total horaire de la main-d'&oelig;uvre","Hourly labour cost")`** *`r tags$sup("(a)(b)")`*</p>

```{r}

genDataTable <- function(data,met,sketch) {
  
  res <- DT::datatable(cbind(country=met[-1],sapply(data[-1,],as.numeric)),
                    rownames=F, container=sketch,
                    options = list(paging=F,searching=F,info=F,
                                   language=list(decimal=","),
                                   columnDefs = list(list(className='dt-right',targets=1:16,
                                                          defaultContent=ifelse(params$lang=="FR",
                                                                                "<i>nd</i>","<i>na</i>"))),
                                   rowCallback=DT::JS(
                                     highlightTableRowByCountry(country=c("fr","ea"),begin=0,end=16,width="1px")
                                   )
                    ),
                    class="compact hover",escape=F) %>%
  formatCurrency(columns=c(2:17),currency="",dec.mark=",",digits=1) %>%
  formatStyle(1,target="row",
              fontWeight=styleEqual(countrynameFR2EN(c("France","Zone euro")),rep("bold",2)),
              color=styleEqual(countrynameFR2EN(c("France","Zone euro")),
                               c(style.color.FR,style.color.EA))) %>%
  formatStyle(5, `box-shadow`='-2px 0 0 black')

  return(res)
  
}

#get data & metadata
data.y.0 <- tail(getData(data.collection,"ZEI010AD1.TXT")[[2]],3)
data.q.0 <- tail(getData(data.collection,"ZEI010AD2.TXT")[[2]],13)
meta <- getData(data.collection,"ZEI010AD1.TXT")[[1]]

#select series
series <- c(1, #variable
            2, #France
            3, #Germany
            4, #Austria
            5, #Belgium
            6, #Spain
            7, #Finland
            8, #Greece
            9, #Ireland
            10, #Italy
            11, #Luxembourg
            12, #Netherlands
            13, #Portugal
            14, #Slovenia
            15) #Euro area 

data.y <- t(data.y.0[,series])
data.q <- t(data.q.0[,series])

#set metadata:
met <- as.character(meta[2,series])
met <- trimws(unlist(lapply(strsplit(met,":"),"[[",1)))
met <- countrynameFR2EN(met)
c.fi <- getCountryByCode("fi",params$lang)
met <- sub(c.fi,paste0(c.fi," <sup><i>(c)</i></sup>"),met,ignore.case=T)
rm(c.fi)

#generate datatable:

#header:

col.q <- as.yearqtr(as.character(data.q[1,]),"%Y-%m")
col.q.y <- as.character(format(col.q,"%Y"))
col.q.q <- as.character(format(col.q,ifelse(params$lang=="FR","T%q","Q%q")))

t <- base::table(col.q.y)
sep.style <- "box-shadow:-2px 0 0 black;"
sketch = htmltools::withTags(table(
  # class = 'display',
  thead(
    tr(
      th(colspan=1,rowspan=3),
      th(colspan=3,rowspan=1,ifelse(params$lang=="FR","Moyenne annuelle","Annual average")),
      th(colspan=13,rowspan=1,ifelse(params$lang=="FR","Glissement annuel","4-quarterly change"),
         style=sep.style)
    ),
    tr(
      lapply(as.character(data.y[1,]), th, rowspan=2),
      lapply(seq_along(t),function(x){th(
        names(t)[[x]],colspan=t[x],
        style=paste0("font-weight:bold; text-align:left; border:none;",ifelse(x==1,sep.style,""))
      )})
    ),
    tr(
      lapply(utils::head(col.q.q,1), th,
             style=paste0("font-weight:normal; ",sep.style)),
      lapply(tail(col.q.q,length(col.q.q)-1), th, style="font-weight:normal; ")
    )
  )
))
rm(t,sep.style)

#end header

#data
data <- as.data.frame(cbind(data.y,data.q), stringsAsFactors=F)
t1 <- genDataTable(data,met,sketch)

#ouput the table
t1

```

<p>&nbsp;</p>
<p>&nbsp;</p>
<p class="titlechart">**`r ifelse(params$lang=="FR","Co&ucirc;t salarial horaire","Hourly wage cost")`** *`r tags$sup("(b)")`*</p>

```{r}

#select series
series <- c(1, #variable
            16, #France
            17, #Germany
            18, #Austria
            19, #Belgium
            20, #Spain
            21, #Finland
            22, #Greece
            23, #Ireland
            24, #Italy
            25, #Luxembourg
            26, #Netherlands
            27, #Portugal
            28, #Slovenia
            29) #Euro area 

data.y <- t(data.y.0[,series])
data.q <- t(data.q.0[,series])

#set metadata:
#same as for t1

#generate datatable:

#header:
#same as for t1

#data:
data <- as.data.frame(cbind(data.y,data.q), stringsAsFactors=F)
t2 <- genDataTable(data,met,sketch)

#ouput the table
t2


```{r eval = T}
<<footer>>
```


